\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-08-23 smurf_paper.tex
More bibliography fixes
Mainly to get SPIE and ASP papers into MN style
Add missing reference to iterative ORAC-DR SCUBA recipe

% journals
\newcommand{\ao}{\rm AO}
\newcommand{\apj}{\rm ApJ}
\newcommand{\apjl}{\rm ApJL}
\newcommand{\apjs}{\rm ApJS}
\newcommand{\aaps}{\rm A$\&$AS}
\newcommand{\aap}{\rm A$\&$A}
\newcommand{\aapr}{\rm A$\&$AR}
\newcommand{\mnras}{\rm MNRAS}
\newcommand{\aj}{\rm Astron. J.}
\newcommand{\araa}{\rm ARAA}
\newcommand{\nat}{\rm Nature}
\newcommand{\pasj}{\rm PASJ}
\newcommand{\pasp}{\rm Publ. Astron. Soc. Pac.}
\newcommand{\prd}{\rm PhRvD}
\newcommand{\ASP}{\rm ASP Conference Series}
\newcommand{\CASP}{\rm Comm. Astrophys. Space Phys.}
\newcommand{\astroph}{\rm astro-ph/}

@@

The third approach adopted here for \scuba\ is a compromise between
the previous two methods. Under the assumption that a significant
portion of the (predominantly low-frequency) non-white noise sources
can be modeled, an iterative solution is obtained for both the
astronomical image and the parameters of the noise model. Since the
remaining (non-modelled) noise sources are assumed to be white, a
single scalar noise may be calculated for all of the data points from
a given bolometer (since the noise at any instant in time is
uncorrelated with others, nor with the data from other bolometers),
greatly simplifying the measurement of noise properties and the
inversion step that is so complicated in the maximum-likelihood
methods. In principle, it should also be possible to recover a wider
dynamic range in angular scales than the simplest ``direct'' methods,
with an increase in calculation time that is merely linear in the
number of iterations needed, while using a comparable amount of
memory. A fast iterative method for handling chopped data from CMB
experiments was described in \citet{wright1996}, and later applied to
chopped SCUBA data by \citet{johnstone2000}, although in each case the
chopping renders the data essentially white without the need to model
additional noise components. More similar to the algorithm described
here was the iterative method for fitting and removing baseline drifts
in SCUBA scan-map data as the astronomical image estimate improved
(...SURF reference?...). The two closest modern relatives of SMURF are the
Comprehensive Reduction Utility for SHARC-2
\citep[CRUSH,][]{kovacs2008}, and the pipeline developed for the
Bolocam Galactic Plane Survey \citep{aguirre2010}.

>>>>

% journals
\newcommand{\ao}{AO}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\apjs}{ApJS}
\newcommand{\aaps}{A$\&$AS}
\newcommand{\aap}{A$\&$A}
\newcommand{\aapr}{A$\&$AR}
\newcommand{\mnras}{MNRAS}
\newcommand{\aj}{A J}
\newcommand{\araa}{\rm ARA\&A}
\newcommand{\nat}{Nat}
\newcommand{\pasj}{PASJ}
\newcommand{\pasp}{PASP}
\newcommand{\prd}{PhRvD}
\newcommand{\ASP}{ASP Conf.\ Ser.~}
\newcommand{\CASP}{\rm Comm. Astrophys. Space Phys.}
\newcommand{\astroph}{\rm astro-ph/}
\newcommand{\spie}{Proc.\ SPIE~}

@@

The third approach adopted here for \scuba\ is a compromise between
the previous two methods. Under the assumption that a significant
portion of the (predominantly low-frequency) non-white noise sources
can be modeled, an iterative solution is obtained for both the
astronomical image and the parameters of the noise model. Since the
remaining (non-modelled) noise sources are assumed to be white, a
single scalar noise may be calculated for all of the data points from
a given bolometer (since the noise at any instant in time is
uncorrelated with others, nor with the data from other bolometers),
greatly simplifying the measurement of noise properties and the
inversion step that is so complicated in the maximum-likelihood
methods. In principle, it should also be possible to recover a wider
dynamic range in angular scales than the simplest ``direct'' methods,
with an increase in calculation time that is merely linear in the
number of iterations needed, while using a comparable amount of
memory. A fast iterative method for handling chopped data from CMB
experiments was described in \citet{wright1996}, and later applied to
chopped SCUBA data by \citet{johnstone2000}, although in each case the
chopping renders the data essentially white without the need to model
additional noise components. More similar to the algorithm described
here was the iterative pipeline recipe for fitting and removing baseline drifts
in SCUBA scan-map data as the astronomical image estimate improved
\citet{1999ASPC..172..171J}. The two closest modern relatives of SMURF are the
Comprehensive Reduction Utility for SHARC-2
\citep[CRUSH,][]{kovacs2008}, and the pipeline developed for the
Bolocam Galactic Plane Survey \citep{aguirre2010}.
